\textsf{Are large language models superhuman chemists?}

### 2024-03-24 src/tex/ms.tex
more review

\paragraph{Study design}
For our initial study we wanted to maximize the response rate given our available resources. 
For this reason, we did not opt for a highly controlled study setting. 
That is, while users were prompted to not use external tools other than a calculator and to not consult with other humans, we do not have any way to verify that the participants complied with those rules. 
Note that users were also allowed to skip questions.

Another aspect of requiring unsupervised question answering is that in real life humans have tools and are able to use them for answering any question of interest. 
In our current study, we prompted users to not use those tools.

>>>>

\paragraph{Study design}
For our initial study we wanted to maximize the response rate given our available resources. 
For this reason, we did not opt for a highly controlled study setting. 
That is, while users were prompted to not use external tools other than a calculator and to not consult other humans, we do not have any way to verify that the participants complied with those rules. 
Note that users were also allowed to skip questions.

Another aspect of requiring unsupervised question answering is that in the real world humans also have tools and are able to use them for answering any question of interest.
